SMASH companion source code repository

### 2018-11-06 analysis/index.Rmd
wflow_publish("index.Rmd")

+ [Illustration of SMASH applied to the "spikes" data set.](spikesdemo.html)

+ [Comparison of signal denoising methods in Gaussian-distributed data
  sets.](gaussian.mean.est.html)

+ [Application of SMASH to motorcycle acceleration data.](motorcycle.html)

+ [Application of SMASH to ChIP-seq data.](chipseq.html)

>>>>

1. [Illustration of SMASH applied to the "spikes" data set.](spikesdemo.html)

2. [Comparison of signal denoising methods in Gaussian-distributed data
   sets.](gaussian.mean.est.html)

3. [Application of SMASH to motorcycle acceleration data.](motorcycle.html)

4. [Application of SMASH to ChIP-seq data.](chipseq.html)
